PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-21 qfenv_paper/qf_environment.tex
Mike's edit's part 2

Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on the evolution of the quenched fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).

@@

We now have a stellar mass complete sample derived from SDSS-{\em GALEX} and PRIMUS data. Since our sample is derived from two different surveys, we account for the disparity in the redshift uncertainty. While PRIMUS provides precise spectroscopic redshifts with $\sigma_{z}/(1+z) \approx 0.5 \%$, due to the higher redshift ranges it probes the uncertainties are significantly greater than that of the SDSS-{\em GALEX} redshifts. In order to have comparable environment measures throughout our redshift range, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its redshift by randomly sampling a normal distribution with standard deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where $z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.

We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method utilizes the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\cite{Noeske:2007aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Then using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \cite{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).

>>>>

Throughout the paper we assume cosmology with $\Omega_{m} = 0.3, \Omega_{\Lambda} = 0.7$, and $H_0 = 70 \: \rm{km} \; \rm{s}^{-1} \rm{Mpc}^{-1}$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on the evolution of the quenched fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and robustness to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis at intermediate redshifts with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).

@@

We now have a stellar mass complete sample derived from SDSS-{\em GALEX} and PRIMUS data. Since our sample is derived from two different surveys, we account for the disparity in the redshift uncertainty. While PRIMUS provides a large number of redshifts out to $z = 1$, due to using a prism instead of a grating, the uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5 \%$) than that of the SDSS-{\em GALEX} redshifts. In order to have comparable environment measures throughout our redshift range, we apply PRIMUS redshift uncertainties to our galaxy sample selected from SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its redshift by randomly sampling a Gaussian distribution with standard deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where $z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.

We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lies above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\cite{Moustakas:2013aa} Figure 1.).
